Easy: 1, 3, 6. Medium: 1, 2 Hard: 1,2,3,4,5

# Setup

```{r, include=FALSE}
library(rethinking)
set.seed(100)
```

```{r}

normalize <- function(values) {
  values / sum(values)
}

p_grid <- seq(from = 0, to = 1, length.out = 1000)
prior <- rep(1, 1000)
likelihood <- dbinom(6, size = 9, prob = p_grid)
posterior <- likelihood * prior
posterior <- posterior / sum(posterior)
plot(p_grid, posterior)

samples <- sample(p_grid, prob = posterior, size = 1e4, replace = TRUE)
```

# 3E1

How much posterior prob likes below p=0.2?

```{r}
sum(samples < 0.2) / length(samples)
```

# 3E3

How much posterior prob lies between p=0.2 and p=0.8?

```{r}
sum(samples > 0.2 & samples < 0.8) / length(samples)
```

# 3E6

Which values of p contain the narrowest interval equal to 66% of the posterior probability?

```{r}
HPDI(samples, prob = 0.66)
```

# Medium

# 3M1

Suppose 8 waters in 15 tosses. Construct the posterior distribution, using grid approximation. Use a flat prior.

```{r}
p_grid <- seq(0, 1, length.out = 1000)
prior <- rep(1, 1000)
likelihood <- dbinom(8, size = 15, prob = p_grid)
posterior <- normalize(prior * likelihood)
plot(p_grid, posterior)
```

# 3M2

Draw 10,000 samples from the grid approximation above. Then use the samples to calculate the 90% HPDI for p. 

```{r}
# Sample from p with probabilities according to posterior distribution
samples <- sample(p_grid, prob = posterior, size = 10000, replace = TRUE)
HPDI(samples, prob = 0.90)
```


# 3H1

male = 1, female = 0. Vector for 100 families

Using grid apprximaiton, compute the posterior distribution for the probability of a birth being a boy. Assum a uniform prior probability. which parameter value maximizes the postior probability?

```{r}
# Load birth1 and birth2 into memory
data(homeworkch3)
```

# 3H2

using `sample` draw 10,000 random parameter values from the posterior distribution you calculated above. use these samples to estimate the 50, 89, and 97 % highest posterior densidty intervalse

# 3H3

Use `rbinom` to simulate 10,000 replicates of 200 births. you should end up with 10000 numbers, each one a count of boys out of 200 births. compare the distirubiot nof predicted numbers of boys to the actual count in the date (111 boys out of 200 births). there are many good ways to visualize the simulations, but the `dens` command is probabliy the easiest way in this case. does it look like the model fits the data well? that is, does the distribution of predictions include the actual observation as a central, likely outcome?

# 3H4

Now compare 10,000 counts of boys from 100 simulatied first borns only to the number of boys in the first births, `birth1`. How does the model look in htis light?

# 3H5

The model assumes that sexs of first and second births are independent. to check this assumption, focus now on second birhs that followed female first borns. compare 10,000 simulated counts of boys to only those second births that followed girls. to do this correctly, you need to count the number of first borns who were girls and simulate that many births, 10,000 times. compare the counts of boys in your simulations to the actual obvserved count of boys following girls. how does the model look in this light? any guesses what is going on in these data?

# Lingering questions

- Why doesn't the documentation for `dbinom` match the usage in the book?